\section{Future Work}

\subsection{Future Agents}

Very early on in our design we decided that our Agents system should be flexible
enough to accommodate a variety of agent types, as not all schemaless data comes
from text log files. We had the following Agents planned, but due to time
constraints were not able to implement them, and felt that our time would be
better spent focusing on processing techniques and UI.

First of all, given our OpenStack background, we would have liked to have built
an Agent that was integrated with OpenStack Ceilometer\cite{ceilometer}, the monitoring and
metrics component of OpenStack. This would have worked in much the same way, but
rather than have the user define a file, they would need to define a Ceilometer
Meter to start watching. After this event processing would have worked in
exactly the same way.

Another consideration was to build an Agent, or extend Bee so that it could tap
into popular logging frameworks. Many applications have now started to move away
from traditional log files, and instead pump data into logging frameworks which
can maintain slightly more structure about a log. Examples include
LogBack\cite{logback}, or Log4j\cite{log4j}.

Furthermore, other open-source projects could be extended to work with our
system, such as FluentD\cite{fluentd}, which has a plugin system that would allow us to
easily build in Apiary support.


\subsection{Hive - Timemachine and Intelligence}

Two future Hive components we considered but were not within the time scale of
the project were Timemachine and Intelligence.

Timemachine would be designed to pull data from the database according to a
query, and then push results onto a message queue in the same order and format
that they originally sent from the agents. A typical use case for this would be
an application that requires a replicated stream of historical data for playing
back events as they happened. This historical playback could be used to analyse
system faults to determine what went wrong.

Intelligence is much more complex and has potentially many more use cases. The
idea behind Intelligence is to provide an API for doing more advanced, deferred
data processing, such as Map Reduce tasks with the log data stored in
Honeycomb. Software like Hadoop\cite{hadoop} would allow for more in depth analysis than
is currently possible with the Lucene implementation in Honeycomb, but would
not work in real-time. The scope of Intelligence could potentially be extended
to include machine learning which we hope would compliment Pheromone with
dynamically generated alerts.
